A Systematic Literature Review on Extensions to Role Based Access Control

### 2013-04-25 paper/sections/core_rbac.tex
minor update (spell) for background

Constrained RBAC incorporates static and dynamic separation of duty relations to the RBAC model. Separation of 
duty relations enforce conflict of interest among roles. This model defines two types of separation of duty relations; static and dynamic.

\begin{itemize}
	\item Static Separation of Duty (SSoD): SSoD restricts the conflicting-role assignments statically that are associated with a user. On situations
	where multiple roles can be associated with a single user and roles $Role_A$ and $Role_B$ are conflicting each other, no permission is given to a user who is assigned to both $Role_A$ and $Role_B$. SSoD is known to be too rigid for practical use in cases where a user should have permissions as either $Role_A$ and $Role_B$.
	\item Dynamic Separation of Duty (DSD): Dynamic SoD is known to be
more flexible than SSD. DSD restricts the conflicting-role assignments dynamically that are associated with a user. On situations
	where multiple roles can be associated with a single user and , given a context, roles $Role_A$ and $Role_B$ are conflicting each other dynamically, no permission is given to a user.	
\end{itemize}

>>>>

Constrained RBAC incorporates static and dynamic separation of duty relations to the RBAC model. Separation of 
duty relations enforces conflict of interest among roles. This model defines two types of separation of duty relations; static and dynamic.

\begin{itemize}
	\item Static Separation of Duty (SSoD): SSoD restricts the conflicting-role assignments statically that are associated with a user. On situations
	where multiple roles can be associated with a single user and roles $Role_A$ and $Role_B$ are conflicting each other, no permission is given to a user who is assigned to both $Role_A$ and $Role_B$. SSoD is known to be too rigid for practical use in cases where a user should have permissions when a user is assigned to both $Role_A$ and $Role_B$.
	\item Dynamic Separation of Duty (DSD): Dynamic SoD is known to be
more flexible than SSD. DSD restricts the conflicting-role assignments dynamically that are associated with a user. On situations
	where multiple roles can be associated with a single user and, roles $Role_A$ and $Role_B$ are conflicting each other dynamically, no permission is given to a user.	
\end{itemize}
